### 2021-06-06 paper/report.tex
Halfway through description of results.

        \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model for translating simulated number to officially recorded cases}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

    \caption{Model description}
    \label{fig:model-description}
\end{figure}

@@

The blue line in Figure~\ref{fig:aggregated_fit} shows the simulated infections based on our model.

Our model:
\begin{itemize}
    \item Fit is great
    \item Multipliers for three categories (how calculated precisely, refer to appendix for breakdown)
    \item Tests fit well
    \item Share known cases, how calculated
\end{itemize}

Reassured by good fit and a couple of external checks (fall vacation regression?), we consider the relative effects of different measures in 2021
\begin{itemize}
    \item Rapid tests,
    \item seasonality
    \item vaccines
\end{itemize}

lessons learned

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:full_new_known_case_cropped}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:full_newly_infected_cropped}
    \end{subfigure}

@@

        \caption{Decomposition of effects for Figure~\ref{fig:full_newly_infected_cropped}.}

        \label{fig:decomposition_scenarios_total_cases}
    \end{subfigure}
    %
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_rapid_tests/full_newly_infected}
        \caption{{\small Effects of different types of testing}}
        \label{fig:decomposition_tests}
    \end{subfigure}

    \caption{The effect of different interventions on recorded and actual infections}
    \label{fig:interventions_broad}

@@

    Note: All aggregates; See S.XXX for statistics by age group and by geographical region.

>>>>

        % \includegraphics[width=\textwidth]{../figures/model_detailed.png}
        \caption{{\small Model for translating simulated number to officially recorded cases}}
        \label{fig:model_for_official_cases}
    \end{subfigure}

    \caption{Model description}
    \label{fig:model-description}

    \floatfoot{
        Note: ...
    }

@@

These developments are characteristic of many countries: The inititial focus on NPIs to slow the spread of the disease has been accompanied by vaccines and a growing acceptance and use of rapid tests. At broadly similar points in time, novel strains of the virus have started to pose additional challenges. The blue line in Figure~\ref{fig:aggregated_fit} shows that our model tracks the simulated infections extremely well. This is also true for infections by age and geographical region, which are shown in the supplementary materials (S.\comment[id=HM]{reference}). We can disentangle various mechanisms due to the distinct temporal variation in the drivers of the pandemic. Next to the stringency index, the three lines in Figure~\ref{fig:stringency_index} summarize how contact reductions, increased hygiene regulations, and seasonality evolved since early September for each of the three broad contact networks. For example, a value of 0.75 for the work multiplier means that if the environment was the same as in September (levels of infection rates, no rapid tests or vaccinations, only the wildtype virus present), infections at the workplace would be reduced by 25\%. This reduction is the product of the effect of contact reductions, increased hygiene regulations, and seasonality. Along with the levels of infections, these measures completely determine the spread of SARS-CoV-2 in 2020.\comment[id=HM]{True?} See Appendix~\comment[id=HM]{Reference} for their individual contributions. Two things are particularly interesting. First, all lines broadly follow the stringency index and they would do so even more if we left out seasonality. Second, the most stringent regulations are associated with the period of strong decreases in new infection beteen late December 2020 and mid-February 2021. The measures were not enough, however, to stop the B.1.1.7 variant from spreading in the subsequent period. The steep drop in recorded cases during May 2021 is associated with rapid tests to X-Y~percent of the population, a vaccination rate that rose from 25\% to 4X\%, and mostly seasonality impacting a fall in the relative infectiousness of contacts.

Reassured by good fit and a couple of external checks (fall vacation regression?), Figure~\ref{fig:2021_scenarios_broad} consider the relative effects of rapid tests, vaccinations, and of seasonality during 2021, assuming NPIs to be the same as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the model fit (blue line, same as in Figure~\ref{fig:aggregated_fit}), a scenario without any of the three factors (x line), and three scenarios turning these factors off one by one.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_new_known_case_cropped}
        \caption{{\small Recorded cases: 2021 scenarios}}
        \label{fig:2021_scenarios_recorded}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/one_off_and_combined/full_newly_infected_cropped}
        \caption{{\small Total cases: 2021 scenarios}}
        \label{fig:2021_scenarios_newly_infected}
    \end{subfigure}

@@

        \caption{Decomposition of effects for Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering

        \includegraphics[width=\textwidth]{../figures/results/figures/scenario_comparisons/effect_of_rapid_tests/full_newly_infected}
        \caption{{\small Effects of different types of testing}}
        \label{fig:2021_scenarios_decomposition_tests}
    \end{subfigure}

    \caption{The effect of different interventions on recorded and actual infections}
    \label{fig:2021_scenarios_broad}

@@

    \floatfoot{
        Note: All aggregates; See S.XXX for statistics by age group and by geographical region.
    }
